### 2010-04-01 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: bring in AllI and allI

However, we still have to define the actual grammar. We obtain it by
evolving $\Desc$ to cope with indexing. The step-by-step
transformation is described in our technical report. The code of
$\IDesc{\!}$ is presented in Figure~\ref{fig:idesc}. The induction
scheme on $\IDesc{\!}$ has the following type:

\[
\begin{array}{@{}ll}
\F{inductionI} : & _{\Bhab{\V{I}}{\Set}}
                   \PITEL{\V{R}}{\V{I} \To \IDesc{\V{I}}}
                   \PI{\V{P}}{\SIGMA{\V{i}}{\V{I}} \IMu{\V{I}}{\V{R}}{\!} \To \Set} \\
                 & (      \PITEL{\V{i}}{\V{I}} 
                          \PI{\V{xs}}{\idescop{\V{R}\: \V{i}}{\V{I}}{\IMu{\V{I}}{\V{R}}{\!}}} \\
                 & \   \idescop{\AllI{\V{I}}
                                     {(\V{R}\: \V{i})}
                                     {(\IMu{\V{I}}{\V{R}}{\!})}
                                     {\V{xs}}}
                               {}
                               {\V{P}} \To
                       \V{P}\: \pair{\V{i}}{\Con{\V{xs}}}{}) \\
                 & \PITEL{\V{i}}{\V{I}}
                   \PI{\V{x}}{\IMu{\V{I}}{\V{R}}{\V{i}}}
                   \V{P}\: \pair{\V{i}}{\V{x}}{}
\end{array}
\]

Where the operator $\AllI{\!}{\!}{\!}{\!}$ is of type:

\[
\AllI{\!}{\!}{\!}{\!} : _{\Bhab{\V{I}}{\Set}}
                        \PITEL{\V{D}}{\IDesc{\V{I}}}
                        \PI{\V{P}}{\V{I} \To \Set}
                        \idescop{\V{D}}{\V{I}}{\V{P}} \To
                        \IDesc{(\SIGMA{\V{i}}{\V{I}} \V{P})} 
\]

The implementation of these operators can be found in the companion
technical report. As for descriptions, we can compute a generic
catamorphism, $\F{cataI}$, from $\F{inductionI}$.

>>>>

However, we still have to define the actual grammar. We obtain it by
evolving $\Desc$ to cope with indexing. \note{Say something about the
  transformation} The code of $\IDesc{\!}$ is presented in
Figure~\ref{fig:idesc}. The induction scheme on $\IDesc{\!}$ has the
following type:

\[\stk{
\begin{array}{@{}ll}
\F{inductionI} : & _{\Bhab{\V{I}}{\Set}}
                   \PITEL{\V{R}}{\V{I} \To \IDesc{\V{I}}}
                   \PI{\V{P}}{\SIGMA{\V{i}}{\V{I}} \IMu{\V{I}}{\V{R}}{\!} \To \Set} \\
                 & (      \PITEL{\V{i}}{\V{I}} 
                          \PI{\V{xs}}{\idescop{\V{R}\: \V{i}}{\V{I}}{\IMu{\V{I}}{\V{R}}{\!}}} \\
                 & \   \idescop{\AllI{\V{I}}
                                     {(\V{R}\: \V{i})}
                                     {(\IMu{\V{I}}{\V{R}}{\!})}
                                     {\V{xs}}}
                               {}
                               {\V{P}} \To
                       \V{P}\: \pair{\V{i}}{\Con{\V{xs}}}{}) \\
                 & \PITEL{\V{i}}{\V{I}}
                   \PI{\V{x}}{\IMu{\V{I}}{\V{R}}{\V{i}}}
                   \V{P}\: \pair{\V{i}}{\V{x}}{}
\end{array} \\
\F{inductionI}\: \V{R}\: \V{P}\: \V{ms}\: \V{i}\: (\Con{\V{xs}}) =  \\
\qquad
    \V{ms}\: \V{i}\: \V{xs}\: (\allI{}
                                    {\V{R}\: \V{i}}
                                    {\IMu{\V{I}}{R}{}}
                                    {\V{P}}
                                    {(\LAM{\pair{\V{i}}{\V{xs}}{}} \F{inductionI}\: \V{R}\: \V{P}\: \V{ms}\: \V{i}\: \V{xs})}
                                    {\V{xs}})
}\]

Where the operators $\AllI{\!}{\!}{\!}{\!}$ and
$\allI{\!}{\!}{\!}{\!}{\!}{\!}$ are defined in
Figure~\ref{fig:allI-predicates}. As for descriptions, we can compute
a generic catamorphism, $\F{cataI}$, from $\F{inductionI}$.

\begin{figure*}

\[
\begin{array}{ll}
%%
\stk{
\begin{array}{@{}ll}
\AllI{\!}{\!}{\!}{\!} : & _{\Bhab{\V{I}}{\Set}}
                          \PITEL{\V{D}}{\IDesc{\V{I}}}
                          \PI{\V{X}}{\V{I} \To \Set} \\
                        & \idescop{\V{D}}{\V{I}}{\V{X}} \To
                          \IDesc{(\TIMES{\V{I}}{\V{X}})}
\end{array} \\
\begin{array}{@{}ll@{\:=\:\:}l}
\AllI{\:}{(\DVar{\V{i}})}{& \V{X}}{\V{x}} &
    \DVar{\pair{\V{i}}{\V{x}}{}} \\
\AllI{\:}{(\DConst{\V{K}})}{& \V{X}}{\V{k}} &
    \DConst{K} \\
\AllI{\:}{(\DProd{\V{D}}{\V{D'}})}{& \V{X}}{\pair{\V{d}}{\V{d'}}{}} &
    \DProd{\AllI{}{\V{D}}{\V{X}}{\V{d}}}{\AllI{}{\V{D'}}{\V{X}}{\V{d'}}} \\
\AllI{\:}{(\DSigma{\V{S}}{\V{T}})}{& \V{X}}{\pair{\V{a}}{\V{b}}{}} &
    \AllI{}{(\V{T}\: \V{a})}{\V{X}}{\V{b}} \\
\AllI{\:}{(\DPi{\V{S}}{\V{T}})}{& \V{X}}{\V{f}} &
    \DPi{\V{S}}{(\LAM{s} \AllI{}{(\V{T}\: \V{s})}{\V{X}}{(\V{f}\: \V{s})})}
\end{array}
}
&
%%
\stk{
\begin{array}{@{}ll}
\allI{\!}{\!}{\!}{\!}{\!}{\!} : & _{\Bhab{\V{I}}{\Set}}
                                  \PITEL{\V{D}}{\IDesc{\V{I}}}
                                  \PITEL{\V{X}}{\V{I} \To \Set} 
                                  \PI{\V{R}}{\TIMES{\V{I}}{\V{X}} \To \Set} \\
                                & (\PI{\V{x}}{\TIMES{\V{I}}{\V{X}}} \V{R}\: \V{x}) \To
                                  \PI{\V{xs}}{\idescop{\V{D}}{}{\V{X}}} 
                                  \idescop{\AllI{}{\V{D}}{\V{X}}{\V{xs}}}{\TIMES{\V{I}}{\V{X}}}{\V{R}}
\end{array} \\
\begin{array}{@{}ll@{\:=\:\:}l}
\allI{\:}{(\DVar{\V{i}})}{& \V{X}}{\V{R}}{\V{P}}{\V{x}} &
    \V{P}\: \pair{\V{i}}{\V{x}}{} \\
\allI{\:}{(\DConst{\V{K}})}{& \V{X}}{\V{R}}{\V{P}}{\V{k}} &
    \V{k} \\
\allI{\:}{(\DProd{\V{D}}{\V{D'}})}{& \V{X}}{\V{R}}{\V{P}}{(\V{d}, \V{d'})} &
    \pair{\allI{}{\V{D}}{\V{X}}{\V{R}}{\V{P}}{\V{d}}}
         {\allI{}{\V{D'}}{\V{X}}{\V{R}}{\V{P}}{\V{d'}}}{} \\
\allI{\:}{(\DSigma{\V{S}}{\V{T}})}{& \V{X}}{\V{R}}{\V{P}}{\pair{\V{a}}{\V{b}}{}} &
    \allI{}{(\V{T}\: \V{a})}{\V{X}}{\V{R}}{\V{P}}{\V{b}} \\
\allI{\:}{(\DPi{\V{S}}{\V{T}})}{& \V{X}}{\V{R}}{\V{P}}{\V{f}} &
    \allI{}{(\V{T}\: \V{a})}{\V{X}}{\V{R}}{\V{P}}{(\V{f}\: \V{a})}
\end{array}
\end{array}
}
\]

\caption{Indexed induction predicates}
\label{fig:allI-predicates}

\end{figure*}
